##團體作業：總統的語言行為

```{r}
library(tm)
```


美國總統
```{r}
a1 <- readLines("1789-Washington.txt")
a2 <- readLines("1793-Washington.txt")
a3 <- readLines("1797-Adams.txt")
a4 <- readLines("1801-Jefferson.txt")
a5 <- readLines("1805-Jefferson.txt")
a6 <- readLines("1809-Madison.txt")
a7 <- readLines("1813-Madison.txt")
a8 <- readLines("1817-Monroe.txt")
a9 <- readLines("1821-Monroe.txt")
a10 <- readLines("1825-Adams.txt")
a11 <- readLines("1829-Jackson.txt")
a12 <- readLines("1833-Jackson.txt")
a13 <- readLines("1837-VanBuren.txt")
a14 <- readLines("1841-Harrison.txt")
a15 <- readLines("1845-Polk.txt")
a16 <- readLines("1849-Taylor.txt")
a17 <- readLines("1853-Pierce.txt")
a18 <- readLines("1857-Buchanan.txt")
a19 <- readLines("1861-Lincoln.txt")
a20 <- readLines("1865-Lincoln.txt")
a21 <- readLines("1869-Grant.txt")
a22 <- readLines("1873-Grant.txt")
a23 <- readLines("1877-Hayes.txt")
a24 <- readLines("1881-Garfield.txt")
a25 <- readLines("1885-Cleveland.txt")
a26 <- readLines("1889-Harrison.txt")
a27 <- readLines("1893-Cleveland.txt")
a28 <- readLines("1897-McKinley.txt")
a29 <- readLines("1901-McKinley.txt")
a30 <- readLines("1905-Roosevelt.txt")
a31 <- readLines("1909-Taft.txt")
a32 <- readLines("1913-Wilson.txt")
a33 <- readLines("1917-Wilson.txt")
a34 <- readLines("1921-Harding.txt")
a35 <- readLines("1925-Coolidge.txt")
a36 <- readLines("1929-Hoover.txt")
a37 <- readLines("1933-Roosevelt.txt")
a38 <- readLines("1937-Roosevelt.txt")
a39 <- readLines("1941-Roosevelt.txt")
a40 <- readLines("1945-Roosevelt.txt")
a41 <- readLines("1949-Truman.txt")
a42 <- readLines("1953-Eisenhower.txt")
a43 <- readLines("1957-Eisenhower.txt")
a44 <- readLines("1961-Kennedy.txt")
a45 <- readLines("1965-Johnson.txt")
a46 <- readLines("1969-Nixon.txt")
a47 <- readLines("1973-Nixon.txt")
a48 <- readLines("1977-Carter.txt")
a49 <- readLines("1981-Reagan.txt")
a50 <- readLines("1985-Reagan.txt")
a51 <- readLines("1989-Bush.txt")
a52 <- readLines("1993-Clinton.txt")
a53 <- readLines("1997-Clinton.txt")
a54 <- readLines("2001-Bush.txt")
a55 <- readLines("2005-Bush.txt")
a56 <- readLines("2009-Obama.txt")
a57 <- readLines("2013-Obama.txt")
```

Washington
```{r}
vc <- VCorpus(VectorSource(c(a1,a2)))
vc <- tm_map(vc, content_transformer(tolower))
vc <- tm_map(vc, stemDocument)
vc <- tm_map(vc, removeWords, stopwords("english"))
dtm <- DocumentTermMatrix(vc)
x0 <- sum(dtm)/2
y0 <- ncol(dtm)/2
```
Adams
```{r}
vc1 <- VCorpus(VectorSource(c(a3,a10)))
vc1 <- tm_map(vc1, content_transformer(tolower))
vc1 <- tm_map(vc1, stemDocument)
vc1 <- tm_map(vc1, removeWords, stopwords("english"))
dtm1 <- DocumentTermMatrix(vc1)
x1 <- sum(dtm1)/2
y1 <- ncol(dtm1)/2
```
Jefferson
```{r}
vc2 <- VCorpus(VectorSource(c(a4,a5)))
vc2 <- tm_map(vc2, content_transformer(tolower))
vc2 <- tm_map(vc2, stemDocument)
vc2 <- tm_map(vc2, removeWords, stopwords("english"))
dtm2 <- DocumentTermMatrix(vc2)
x2 <- sum(dtm2)/2
y2 <- ncol(dtm2)/2
```
Madison
```{r}
vc3 <- VCorpus(VectorSource(c(a6,a7)))
vc3 <- tm_map(vc3, content_transformer(tolower))
vc3 <- tm_map(vc3, stemDocument)
vc3 <- tm_map(vc3, removeWords, stopwords("english"))
dtm3 <- DocumentTermMatrix(vc3)
x3 <- sum(dtm3)/2
y3 <- ncol(dtm3)/2
```
Monroe
```{r}
vc4 <- VCorpus(VectorSource(c(a8,a9)))
vc4 <- tm_map(vc4, content_transformer(tolower))
vc4 <- tm_map(vc4, stemDocument)
vc4 <- tm_map(vc4, removeWords, stopwords("english"))
dtm4 <- DocumentTermMatrix(vc4)
x4 <- sum(dtm4)/2
y4 <- ncol(dtm4)/2
```
Jackson
```{r}
vc5 <- VCorpus(VectorSource(c(a11,a12)))
vc5 <- tm_map(vc5, content_transformer(tolower))
vc5 <- tm_map(vc5, stemDocument)
vc5 <- tm_map(vc5, removeWords, stopwords("english"))
dtm5 <- DocumentTermMatrix(vc5)
x5 <- sum(dtm5)/2
y5 <- ncol(dtm5)/2
```
VanBuren
```{r}
vc6 <- VCorpus(VectorSource(c(a13)))
vc6 <- tm_map(vc6, content_transformer(tolower))
vc6 <- tm_map(vc6, stemDocument)
vc6 <- tm_map(vc6, removeWords, stopwords("english"))
dtm6 <- DocumentTermMatrix(vc6)
x6 <- sum(dtm6)
y6 <- ncol(dtm6)
```
Harrison
```{r}
vc7 <- VCorpus(VectorSource(c(a14)))
vc7 <- tm_map(vc7, content_transformer(tolower))
vc7 <- tm_map(vc7, stemDocument)
vc7 <- tm_map(vc7, removeWords, stopwords("english"))
dtm7 <- DocumentTermMatrix(vc7)
x7 <- sum(dtm7)
y7 <- ncol(dtm7)
```
Polk
```{r}
vc8 <- VCorpus(VectorSource(c(a15)))
vc8 <- tm_map(vc8, content_transformer(tolower))
vc8 <- tm_map(vc8, stemDocument)
vc8 <- tm_map(vc8, removeWords, stopwords("english"))
dtm8 <- DocumentTermMatrix(vc8)
x8 <- sum(dtm8)
y8 <- ncol(dtm8)
```
Taylor
```{r}
vc9 <- VCorpus(VectorSource(c(a16)))
vc9 <- tm_map(vc9, content_transformer(tolower))
vc9 <- tm_map(vc9, stemDocument)
vc9 <- tm_map(vc9, removeWords, stopwords("english"))
dtm9 <- DocumentTermMatrix(vc9)
x9 <- sum(dtm9)
y9 <- ncol(dtm9)
```
Pierce
```{r}
vc10 <- VCorpus(VectorSource(c(a17)))
vc10 <- tm_map(vc10, content_transformer(tolower))
vc10 <- tm_map(vc10, stemDocument)
vc10 <- tm_map(vc10, removeWords, stopwords("english"))
dtm10 <- DocumentTermMatrix(vc10)
x10 <- sum(dtm10)
y10 <- ncol(dtm10)
```
Buchanan
```{r}
vc11 <- VCorpus(VectorSource(c(a18)))
vc11 <- tm_map(vc11, content_transformer(tolower))
vc11 <- tm_map(vc11, stemDocument)
vc11 <- tm_map(vc11, removeWords, stopwords("english"))
dtm11 <- DocumentTermMatrix(vc11)
x11 <- sum(dtm11)
y11 <- ncol(dtm11)
```
Lincoln
```{r}
vc12 <- VCorpus(VectorSource(c(a19,a20)))
vc12 <- tm_map(vc12, content_transformer(tolower))
vc12 <- tm_map(vc12, stemDocument)
vc12 <- tm_map(vc12, removeWords, stopwords("english"))
dtm12 <- DocumentTermMatrix(vc12)
x12 <- sum(dtm12)/2
y12 <- ncol(dtm12)/2
```
Grant
```{r}
vc13 <- VCorpus(VectorSource(c(a21,a22)))
vc13 <- tm_map(vc13, content_transformer(tolower))
vc13 <- tm_map(vc13, stemDocument)
vc13 <- tm_map(vc13, removeWords, stopwords("english"))
dtm13 <- DocumentTermMatrix(vc13)
x13 <- sum(dtm13)/2
y13 <- ncol(dtm13)/2
```
Hayes
```{r}
vc14 <- VCorpus(VectorSource(c(a23)))
vc14 <- tm_map(vc14, content_transformer(tolower))
vc14 <- tm_map(vc14, stemDocument)
vc14 <- tm_map(vc14, removeWords, stopwords("english"))
dtm14 <- DocumentTermMatrix(vc14)
x14 <- sum(dtm14)
y14 <- ncol(dtm14)
```
Garfield
```{r}
vc15 <- VCorpus(VectorSource(c(a24)))
vc15 <- tm_map(vc15, content_transformer(tolower))
vc15 <- tm_map(vc15, stemDocument)
vc15 <- tm_map(vc15, removeWords, stopwords("english"))
dtm15 <- DocumentTermMatrix(vc15)
x15 <- sum(dtm15)
y15 <- ncol(dtm15)
```
Cleveland
```{r}
vc16 <- VCorpus(VectorSource(c(a25,a27)))
vc16 <- tm_map(vc16, content_transformer(tolower))
vc16 <- tm_map(vc16, stemDocument)
vc16 <- tm_map(vc16, removeWords, stopwords("english"))
dtm16 <- DocumentTermMatrix(vc16)
x16 <- sum(dtm16)/2
y16 <- ncol(dtm16)/2
```
Harrison
```{r}
vc17 <- VCorpus(VectorSource(c(a26)))
vc17 <- tm_map(vc17, content_transformer(tolower))
vc17 <- tm_map(vc17, stemDocument)
vc17 <- tm_map(vc17, removeWords, stopwords("english"))
dtm17 <- DocumentTermMatrix(vc17)
x17 <- sum(dtm17)
y17 <- ncol(dtm17)
```
McKinley
```{r}
vc18 <- VCorpus(VectorSource(c(a28,a29)))
vc18 <- tm_map(vc18, content_transformer(tolower))
vc18 <- tm_map(vc18, stemDocument)
vc18 <- tm_map(vc18, removeWords, stopwords("english"))
dtm18 <- DocumentTermMatrix(vc18)
x18 <- sum(dtm18)/2
y18 <- ncol(dtm18)/2
```
Roosevelt
```{r}
vc19 <- VCorpus(VectorSource(c(a30,a37,a38,a39,a40)))
vc19 <- tm_map(vc19, content_transformer(tolower))
vc19 <- tm_map(vc19, stemDocument)
vc19 <- tm_map(vc19, removeWords, stopwords("english"))
dtm19 <- DocumentTermMatrix(vc19)
x19 <- sum(dtm19)/5
y19 <- ncol(dtm19)/5
```
Talf
```{r}
vc20 <- VCorpus(VectorSource(c(a31)))
vc20 <- tm_map(vc20, content_transformer(tolower))
vc20 <- tm_map(vc20, stemDocument)
vc20 <- tm_map(vc20, removeWords, stopwords("english"))
dtm20 <- DocumentTermMatrix(vc20)
x20 <- sum(dtm20)
y20 <- ncol(dtm20)
```
Wilson
```{r}
vc21 <- VCorpus(VectorSource(c(a32,a33)))
vc21 <- tm_map(vc21, content_transformer(tolower))
vc21 <- tm_map(vc21, stemDocument)
vc21 <- tm_map(vc21, removeWords, stopwords("english"))
dtm21 <- DocumentTermMatrix(vc21)
x21 <- sum(dtm21)/2
y21 <- ncol(dtm21)/2
```
Harding
```{r}
vc22 <- VCorpus(VectorSource(c(a34)))
vc22 <- tm_map(vc22, content_transformer(tolower))
vc22 <- tm_map(vc22, stemDocument)
vc22 <- tm_map(vc22, removeWords, stopwords("english"))
dtm22 <- DocumentTermMatrix(vc22)
x22 <- sum(dtm22)
y22 <- ncol(dtm22)
```
Coolidge
```{r}
vc23 <- VCorpus(VectorSource(c(a35)))
vc23 <- tm_map(vc23, content_transformer(tolower))
vc23 <- tm_map(vc23, stemDocument)
vc23 <- tm_map(vc23, removeWords, stopwords("english"))
dtm23 <- DocumentTermMatrix(vc23)
x23 <-sum(dtm23)
y23 <- ncol(dtm23)
```
Hoover
```{r}
vc24 <- VCorpus(VectorSource(c(a36)))
vc24 <- tm_map(vc24, content_transformer(tolower))
vc24 <- tm_map(vc24, stemDocument)
vc24 <- tm_map(vc24, removeWords, stopwords("english"))
dtm24 <- DocumentTermMatrix(vc24)
x24 <- sum(dtm24)
y24 <- ncol(dtm24)
```
Truman
```{r}
vc25 <- VCorpus(VectorSource(c(a41)))
vc25 <- tm_map(vc25, content_transformer(tolower))
vc25 <- tm_map(vc25, stemDocument)
vc25 <- tm_map(vc25, removeWords, stopwords("english"))
dtm25 <- DocumentTermMatrix(vc25)
x25 <- sum(dtm25)
y25 <- ncol(dtm25)
```
Eisenhower
```{r}
vc26 <- VCorpus(VectorSource(c(a42,a43)))
vc26 <- tm_map(vc26, content_transformer(tolower))
vc26 <- tm_map(vc26, stemDocument)
vc26 <- tm_map(vc26, removeWords, stopwords("english"))
dtm26 <- DocumentTermMatrix(vc26)
x26 <- sum(dtm26)/2
y26 <- ncol(dtm26)/2
```
Kennedy
```{r}
vc27 <- VCorpus(VectorSource(c(a44)))
vc27 <- tm_map(vc27, content_transformer(tolower))
vc27 <- tm_map(vc27, stemDocument)
vc27 <- tm_map(vc27, removeWords, stopwords("english"))
dtm27 <- DocumentTermMatrix(vc27)
x27 <- sum(dtm27)
y27 <- ncol(dtm27)
```
Johnson
```{r}
vc28 <- VCorpus(VectorSource(c(a45)))
vc28 <- tm_map(vc28, content_transformer(tolower))
vc28 <- tm_map(vc28, stemDocument)
vc28 <- tm_map(vc28, removeWords, stopwords("english"))
dtm28 <- DocumentTermMatrix(vc28)
x28 <- sum(dtm28)
y28 <- ncol(dtm28)
```
Nixon
```{r}
vc29 <- VCorpus(VectorSource(c(a46,a47)))
vc29 <- tm_map(vc29, content_transformer(tolower))
vc29 <- tm_map(vc29, stemDocument)
vc29 <- tm_map(vc29, removeWords, stopwords("english"))
dtm29 <- DocumentTermMatrix(vc29)
x29 <- sum(dtm29)/2
y29 <- ncol(dtm29)/2
```
Carter
```{r}
vc30 <- VCorpus(VectorSource(c(a48)))
vc30 <- tm_map(vc30, content_transformer(tolower))
vc30 <- tm_map(vc30, stemDocument)
vc30 <- tm_map(vc30, removeWords, stopwords("english"))
dtm30 <- DocumentTermMatrix(vc30)
x30 <- sum(dtm30)
y30 <- ncol(dtm30)
```
Reagan
```{r}
vc31 <- VCorpus(VectorSource(c(a49,a50)))
vc31 <- tm_map(vc31, content_transformer(tolower))
vc31 <- tm_map(vc31, stemDocument)
vc31 <- tm_map(vc31, removeWords, stopwords("english"))
dtm31 <- DocumentTermMatrix(vc31)
x31 <- sum(dtm31)/2
y31 <- ncol(dtm31)/2
```
Bush
```{r}
vc32 <- VCorpus(VectorSource(c(a51,a54,a55)))
vc32 <- tm_map(vc32, content_transformer(tolower))
vc32 <- tm_map(vc32, stemDocument)
vc32 <- tm_map(vc32, removeWords, stopwords("english"))
dtm32 <- DocumentTermMatrix(vc32)
x32 <- sum(dtm32)/3
y32 <- ncol(dtm32)/3
```
Clinton
```{r}
vc33 <- VCorpus(VectorSource(c(a52,a53)))
vc33 <- tm_map(vc33, content_transformer(tolower))
vc33 <- tm_map(vc33, stemDocument)
vc33 <- tm_map(vc33, removeWords, stopwords("english"))
dtm33 <- DocumentTermMatrix(vc33)
x33 <- sum(dtm33)/2
y33 <- ncol(dtm33)/2
```
Obama
```{r}
vc34 <- VCorpus(VectorSource(c(a56,a57)))
vc34 <- tm_map(vc34, content_transformer(tolower))
vc34 <- tm_map(vc34, stemDocument)
vc34 <- tm_map(vc34, removeWords, stopwords("english"))
dtm34 <- DocumentTermMatrix(vc34)
x34 <- sum(dtm34)/2
y34 <- ncol(dtm34)/2
```

```{r}
Presidence_name <- c("Washington","Adams","Jefferson","Madison","Monroe","Jackson","VanBuren","Harrison","Polk","Taylor","Pierce","Buchanan","Lincoln","Grant","Hayes","Garfield","Cleveland","Harrison","McKinley","Roosevelt","Talf","Wilson","Harding","Coolidge","Hoover","Truman","Eisenhower","Kennedy","Johnson","Nixon","Carter","Reagan","Bush","Clinton","Obama")
Total_words <- c(x0,x1,x2,x3,x4,x5,x6,x7,x8,x9,x10,x11,x12,x13,x14,x15,x16,x17,x18,x19,x20,x21,x22,x23,x24,x25,x26,x27,x28,x29,x30,x31,x32,x33,x34)
Different_words <- c(y0,y1,y2,y3,y4,y5,y6,y7,y8,y9,y10,y11,y12,y13,y14,y15,y16,y17,y18,y19,y20,y21,y22,y23,y24,y25,y26,y27,y28,y29,y30,y31,y32,y33,y34)
final <- data.frame(Presidence_name,Total_words,Different_words)
final$Total_words <- round(final$Total_words)
final$Different_words <- round(final$Different_words)
print(final)
```


####The Presidence with most words in speaking 
##Harrison with 3869 words


####The Presidence with most different words in speaking 
##Harrison with 1646 words



